---
title: "Lab 7 rank-based test"
author: "Caio Vianna"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi this is Caio and I created this repo and markdown document

COLLABORATOR (TERESA) is going to make some histograms.

```{r}

# load packages and read in data

library (tidyverse)

kermit <- read_csv("kermit.csv")

# make a histogram 

kermit_hist <- ggplot(kermit, aes(x=Score.pre)) +
  geom_histogram() +
  facet_wrap(~ Gender)


kermit_hist
```

Creator: doing some rank-based tests

# Is there a significant difference in pre-talk kermit scores for males an females?

# unpaired: Mann-Whitney U

```{r}

mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

mwu_kermit

```


COLLABORATOR: 
Compare pre- talk and post-talk ranks
Is there a significant difference in Kermit ranks for pre-talk and post-talk scores (ignoring all other variables)?

This is a two tailed test because there is no directionality implied in the way that the question is asked. 

Null: No.

```{r}

wsr_kermit <- wilcox.test(kermit$Score.pre,kermit$Score.post, paired=TRUE)
wsr_kermit

# There is no significant difference in Kermit rankings before and after his talk (statistical summary...)

```








